### 2015-06-22 chapters/ipa_meets_unicode.tex
adding (lax) IPA sanctioned symbols

TO DO:
[ordering]
[boundaries, stress, intonation]
[additions]

@@

   \item \textsc{IPA letters} \newline
        The 107 different IPA letters as allowed in strict-IPA encoding are
        listed in Table~\ref{tab:ipa_letters} starting on
        page~\pageref{tab:ipa_letters}.
  \item \textsc{IPA diacritics} \newline The 36 different IPA diacritics and
        tone markers (both Unicode Modifier Letters and Combining Diacritical
        Marks) as allowed in strict-IPA encoding are listed in
        Table~\ref{tab:ipa_diacritics} starting on
        page~\pageref{tab:ipa_diacritics}.
  \item \textsc{IPA remainders} \newline The 16 remaining IPA symbols
        (boundary, stress, tone letters and intonation markers) as allowed in strict-IPA
        encoding are listed in Table~\ref{tab:ipa_leftovers} on
        page~\pageref{tab:ipa_leftovers}. 
  \item \textsc{IPA additions} \newline
        The 10 proposed additions to the IPA are listed in
        Table~\ref{tab:ipa_additions} on page~\pageref{tab:ipa_additions}.

@@

\newpage
\input{tables/unicode_letters}
\input{tables/unicode_diacritics} 
\input{tables/unicode_boundaries}
\input{tables/unicode_additions}

>>>>

TO DO:
[ordering]
[boundaries, stress, intonation]
[laxIPA]
[additions]

@@

  \item \textsc{IPA letters} \newline
        The 107 different IPA letters as allowed in strict-IPA encoding are
        listed in Table~\ref{tab:ipa_letters} starting on
        page~\pageref{tab:ipa_letters}.
  \item \textsc{IPA diacritics} \newline The 36 different IPA diacritics and
        tone markers (both Unicode Modifier Letters and Combining Diacritical
        Marks) as allowed in strict-IPA encoding are listed in
        Table~\ref{tab:ipa_diacritics} starting on
        page~\pageref{tab:ipa_diacritics}.
  \item \textsc{IPA remainders} \newline The 16 remaining IPA symbols
        (boundary, stress, tone letters and intonation markers) as allowed in strict-IPA
        encoding are listed in Table~\ref{tab:ipa_leftovers} on
        page~\pageref{tab:ipa_leftovers}.
  \item \textsc{IPA alternatives} \newline The 16 additional symbols as allowed in
        lax-IPA encoding are listed in Table~\ref{tab:ipa_lax} on
        page~\pageref{tab:ipa_lax}.     
  \item \textsc{optional IPA additions} \newline
        The 10 proposed additions to the IPA are listed in
        Table~\ref{tab:ipa_additions} on page~\pageref{tab:ipa_additions}.

@@

\newpage
\input{tables/unicode_letters}
\input{tables/unicode_diacritics}
\input{tables/unicode_boundaries}
\input{tables/unicode_lax}
\input{tables/unicode_additions}
